\documentclass[10pt]{article}
\input{build_settings}

\begin{document}

\input{header}

% work experience
% ---------------

\cvsection{EDUCATION}

\cvitem{
    \cvdurationstyle{Aug. 2019 -- May 2023}
}{
    \cvtitle{PhD of Engineering in Computer Engineering}

    Purdue University, West Lafayette, Indiana

    \begin{itemize}[leftmargin=*]
        \item \textit{Area of Study:} Machine Learning and Artificial Intelligence with focus in Generative Models
        \item GPA: 3.67
        % \item \textit{PhD Thesis:} 
    \end{itemize}
}
\cvitem{
    \cvdurationstyle{Aug. 2015 -- May 2019}
}{
    \cvtitle{Bachelor's of Science in Electrical Engineering}

    Purdue University, West Lafayette, Indiana

    \begin{itemize}[leftmargin=*]
        \item \textit{Area of Study:} Automatic Controls
        \item GPA: 3.14
    \end{itemize}
}

\cvsection{RESEARCH EXPERIENCE}

\cvitem{
    \cvdurationstyle{Aug. 2019 -- Present}
}{
    \cvtitle{Research Assistant for Destructive Density Learners Project}

    \textit{Advisors:} Dr. David Inouye and Dr. Saurabh Bagchi
    \\West Lafayette, Indiana
    
    
    I am designing and building a machine learning model using Deep Density Destructors to build a generative model for the purpose of anomaly detection in data with the constraint that both the test and training data might be high dimensional and containing missing values. The model is being developed with the goal of being a modular learning scheme which can be implemented and tested on edge devices in a network.

    
}

\cvitem{
    \cvdurationstyle{May 2018 -- May. 2019}
    }{
    \cvtitle{Lead Undergraduate Researcher for Prosthetic Haptic Interfaces Project}
    \textit{Advisor: Dr. Hong Tan}
    \\West Lafayette, Indiana
    
    
    Here I began an international collaborative research project with Centro di Ricerca "E. Piaggio" Lab from University of Pisa, Italy for testing the effects of encoding the state of a prosthetic hand by softly stretching the skin of a user's upper arm to simulate proprioceptive feedback of a biological hand. In addition to leading the group, I developed the GUI for automatic data collection and parsing with the human subjects, as well as, assisting in the design and manufacturing of the wearable motorized device.
    }

\cvsection{WORK EXPERIENCE}

\cvitem{
    \cvdurationstyle{Jan. 2019 -- Aug. 2019}
}{
    \cvtitle{Software and Embedded Electrical Engineer}

    Indiana Microelectronics, West Lafayette, Indiana


    In this role, I developed a genetic algorithm  to automate and optimize the design of transmission zero filters using parallelizable simulations for a phased-array system for a project with Lockheed Martin. I also designed a system to test and collect temperature drift data for a closed-loop piezoelectric motor. 
}

\cvitem{
    \cvdurationstyle{Aug. 2019 -- Dec. 2019}
}{
    \cvtitle{Graduate Teaching Assistant for ECE Senior Design}

    Purdue University, West Lafayette, Indiana

    As a GTA, I directed a lab of 16 students through the process of bringing a hardware/software project from idea to a product. During this process, I acted as both a Senior Engineer and Manager to four different projects simultaneously. In addition to my usual lecturing/grading duties, I also held an external workshop for Python, PCB design in Altium, and device/system testing.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  SHORTEN TO ONE PAGE =====================================================
\if\onepage1
\else

\cvitem{
    \cvdurationstyle{May. 2017 -- Aug. 2017}
}{
    \cvtitle{Embedded Electrical R\&D Testing Engineer}

    Stryker Corp., Fort Lauderdale, Florida
    
    In this position, I created a script for measuring and visualizing live power consumption for various loads on an arm-assisted surgical robot using MATLAB. I also designed and laid out a PCB for high frequency and large duration measurements to be used in the load measuring process with using a NI-DAQ as an intermediary. 
    
}

% \cvitem{
%     \cvdurationstyle{Aug. 1999 -- Dec. 1999}
% }{
%     \cvtitle{PLACEHOLDER}

%     Purdue University, West Lafayette, Indiana

%     \begin{itemize}[leftmargin=*]
%         \item Did this one thing which can be seen here \if\online1~\href{https://google.com}{Google} and \href{https://bing.com}{Bing}\else~Google and Bing\fi~for searching the interwebs.
%         \item Oh I did this too.
%     \end{itemize}
% }


% \cvsection{PUBLICATIONS}

% \cvitem{
%     \cvdurationstyle{}
% }{
%     % \if\cv
%     \begin{itemize}[leftmargin=*]
%         \item \textbf{Sean Kulinski}, Not Sean Kulinski \if\online1~\href{https://google.com}{Google}\else~Google\fi, This is my paper 2020.
%         \item Not Sean Kulinski \textbf{Sean Kulinski}, \if\online1~\href{https://google.com}{Google}\else~Google\fi, This is my second paper 2020.
%     \end{itemize}

% }


% \if\cv1
%     \cvsection{Other Experience}
    
    % \cvitem{
    %     \cvdurationstyle{Aug 2016 - May 2017}
    % }{
    %     \cvtitle{Alpha Tau Omega - Leadership Development Fraternity: Gamma Chapter, Purdue University}
        
    %     Recruitment Chair and Executive Board Member
    
    %     \begin{itemize}[leftmargin=*]
    %         \item Elected member of the executive board by chapter.
    %         \item Created new recruitment initiative, planned, and hosted recruitment events.
    %         \item Managed database of potential new members for easing of voting on acceptance of new members. 
    %     \end{itemize}
        
    % }
\fi
% END ONE PAGE =================================
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


    
    
% skills
% ------
\cvsection{SKILLS}

\vspace{\cvbetweensectionandheadingextraskipamount}

\cvitem{
    \cvheadingstyle{Programming Languages and Frameworks}
}{
    Python, MATLAB, C, LaTeX, Bash, Batch, VBA, Git, GitHub, Docker, SCPI, Octave, Numpy, Pandas, Scikit Learn, Scipy, OpenCV, Excel, Pytorch, Linux, Jupyter, Anaconda, STM32, Altium, EagleCAD, OrCAD, AutoDesk Fusion360, CATIA
}

\vspace{\cvbetweensectionandheadingextraskipamount}
\cvitem{
    \cvheadingstyle{More Skills}}
    {Leading and working within teams, strong mathematics background, data analysis, all Microsoft Office, product research and design}
    

%Leadership and Activities%%%%%%%%%%%
\cvsection{LEADERSHIP AND ACTIVITIES}
\vspace{\cvbetweensectionandheadingextraskipamount}

\cvitem{
    \cvdurationstyle{2015 -- Present}}
    {Study Abroad in London, England with CAPA Global Health Networt (2018), Executive Board of Alpha Tau Omega Leadership Development Fraternity (2017), Volunteer at Natalie's Second Chance Dog Shelter (Present), Eagle Scout and Avid Backpacker (Present)}

\cvsection{REFERENCES}
\vspace{\cvbetweensectionandheadingextraskipamount}
\cvitem{
    \cvdurationstyle{}}
    {
    To hear more about my experience and skills, please contact me or one of my references below.
    \vspace{\cvbetweensectionandheadingextraskipamount}
    \\
    David Inouye, Ph.D.
    \begin{itemize}
        \item \textit{Destructive Density Learners Project Co-Advisor (Current Research Advisor)}
        \item \textit{Assistant Professor in School of Electrical and Computer Engineering}
        \item\href{mailto:dinouye@purdue.edu}{\textit{dinouye@purdue.edu}}
        \end{itemize}
    Saurabh Bagchi, Ph.D.
    \begin{itemize}
        \item \textit{Destructive Density Learners Project Co-Advisor (Current Research Advisor)}
        \item \textit{Professor in School of Electrical and Computer Engineering and in Computer Science (by courtesy) at Purdue University and Assistant Director of CERIAS security center}
        \item\href{mailto:sbagchi@purdue.edu}{\textit{sbagchi@purdue.edu}}
        \end{itemize}
    Hong Tan, Ph.D.
        \begin{itemize}
        \item \textit{Prosthetic Haptic Interfaces Project Advisor (Undergraduate Research Advisor)}
        \item \textit{Professor in School of Electrical and Computer Engineering at Purdue University and Mechanical Engineering (by courtesy) and head of HIRL lab}
        \item\href{mailto:hongtan@purdue.edu}{\textit{hongtan@purdue.edu}}
        \end{itemize}
    Steve Cuppy, M.S.
        \begin{itemize}
        \item \textit{Project Manager for Lockheed Martin Project}
        \item \textit{Business Development, Indiana Micro}
        \item\href{mailto:cuppys@indianamicro.com}{\textit{cuppys@indianamicro.com}}
        \end{itemize}
    }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}