\documentclass[10pt]{article}
\input{build_settings}

\begin{document}

\input{header}

% work experience
% ---------------

\cvsection{EDUCATION}

\cvitem{
    \cvdurationstyle{Aug. 2019 -- May 2023}
}{
    \cvtitle{PhD of Engineering in Computer Engineering}

    Purdue University, West Lafayette, Indiana

    \begin{itemize}[leftmargin=*]
        \item \textit{Area of Study:} Machine Learning and Artificial Intelligence -- GPA: 3.67
        % \item \textit{PhD Thesis:} 
    \end{itemize}
}
\cvitem{
    \cvdurationstyle{Aug. 2015 -- May 2019}
}{
    \cvtitle{Bachelor's of Science in Electrical Engineering}

    Purdue University, West Lafayette, Indiana

    \begin{itemize}[leftmargin=*]
        \item \textit{Area of Study:} Automatic Controls
    \end{itemize}
}

\cvsection{RESEARCH EXPERIENCE}

\cvitem{
    \cvdurationstyle{Aug. 2019 -- Present}
}{
    \cvtitle{Research Assistant for Destructive Density Learners Project}

    \textit{Advisors:} Dr. David Inouye and Dr. Saurabh Bagchi
    \\West Lafayette, Indiana

    \begin{itemize}[leftmargin=*]
        \item Using novel technique to model distributions to detect anomalies using deep density destructors.
        \item Developing robust models even in the event of lost or adversarially changed data.
        \item Creating a modular learning scheme for general machine learning which can be implemented on edge devices.
    \end{itemize}
    
}

\cvitem{
    \cvdurationstyle{May 2018 - Aug. 2019}
    }{
    \cvtitle{Lead Undergraduate Researcher for Prosthetic Haptic Interfaces Project}
    \textit{Advisor: Dr. Hong Tan}
    \\West Lafayette, Indiana
    
    \begin{itemize}[leftmargin=*]
        \item Began international collaborative research project with Centro di Ricerca "E. Piaggio" Lab from University of Pisa, Italy.
        \item Lead experiment to test effects of proprioceptive feedback of prosthesis delivered via skin stretching for upper limb prostheses.
        \item Developed GUI for data collection for human subjects with automatic data parsing.
        \item Designed and manufactured wearable motorized device to encode the state of robotic hand.
    \end{itemize}
    }

\cvsection{WORK EXPERIENCE}

\cvitem{
    \cvdurationstyle{Jan. 2019 -- Aug. 2019}
}{
    \cvtitle{Software and Embedded Electrical Engineer}

    Indiana Microelectronics, West Lafayette, Indiana

    \begin{itemize}[leftmargin=*]
        \item Developed Genetic Algorithm to automate and optimize design of transmission zero filters for Lockheed Martin.
        \item Designed automated testing of temperature drift for a closed-loop linear piezoelectric motor.
        \item Oversaw testing, calibration, and reworks for a phased-array filter system.
    \end{itemize}
}

\cvitem{
    \cvdurationstyle{Aug. 2019 -- Dec. 2019}
}{
    \cvtitle{Graduate Teaching Assistant for ECE Senior Design}

    Purdue University, West Lafayette, Indiana

    \begin{itemize}[leftmargin=*]
        \item Directed a lab of 16 students through the process of bringing a hardware/software project from idea to product.
        \item Acted as a Senior Engineer and Manager to four different projects simultaneously.
        \item Held external workshops in various ECE skills such as Python, PCB design, and device testing.
    \end{itemize}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  SHORTEN TO ONE PAGE =====================================================
\if\onepage1
\else

\cvitem{
    \cvdurationstyle{Aug. 2018 -- Dec. 2019}
}{
    \cvtitle{Embedded Electrical R\&D Testing Engineer}

    Stryker Corp., Fort Lauderdale, Florida

    \begin{itemize}[leftmargin=*]
        \item Created dynamic power consumption measuring tool for loads on an arm-assisted surgical robot.
        \item Designed, laid out, and printed circuit board for high frequency and large duration measurements.
        \item Created tool for automatic formatting and parsing of raw input data for the purpose of immediate analysis. 
    \end{itemize}
}

\cvitem{
    \cvdurationstyle{Aug. 1999 -- Dec. 1999}
}{
    \cvtitle{PLACEHOLDER}

    Purdue University, West Lafayette, Indiana

    \begin{itemize}[leftmargin=*]
        \item Did this one thing which can be seen here \if\online1~\href{https://google.com}{Google} and \href{https://bing.com}{Bing}\else~Google and Bing\fi~for searching the interwebs.
        \item Oh I did this too.
    \end{itemize}
}


\cvsection{PUBLICATIONS}

\cvitem{
    \cvdurationstyle{}
}{
    % \if\cv
    \begin{itemize}[leftmargin=*]
        \item \textbf{Sean Kulinski}, Not Sean Kulinski \if\online1~\href{https://google.com}{Google}\else~Google\fi, This is my paper 2020.
        \item Not Sean Kulinski \textbf{Sean Kulinski}, \if\online1~\href{https://google.com}{Google}\else~Google\fi, This is my second paper 2020.
    \end{itemize}

}


\if\cv1
    \cvsection{FRATERNITY LEADERSHIP}
    
    \cvitem{
        \cvdurationstyle{Aug 2016 - May 2017}
    }{
        \cvtitle{Alpha Tau Omega - Leadership Development Fraternity: Gamma Chapter, Purdue University}
        
        Recruitment Chair and Executive Board Member
    
        \begin{itemize}[leftmargin=*]
            \item Elected member of the executive board by chapter.
            \item Created new recruitment initiative, planned, and hosted recruitment events.
            \item Managed database of potential new members for easing of voting on acceptance of new members. 
        \end{itemize}
        
    }
\fi
% END ONE PAGE =================================
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi


    
    
% skills
% ------
\cvsection{SKILLS}

\vspace{\cvbetweensectionandheadingextraskipamount}

\cvitem{
    \cvheadingstyle{Programming Languages and Frameworks}
}{
    Python, MATLAB, C, Octave, Bash, Batch, VBA, HTML, Git, GitHub, Numpy, Pandas, Scikit Learn, Scipy, Django, OpenCV, Excel, Pytorch, TensorFlow, Linux, Jupyter, Anaconda, STM32, Altium, EagleCAD, OrCAD, AutoDesk Fusion360, CATIA
}

\vspace{\cvbetweensectionandheadingextraskipamount}
\cvitem{
    \cvheadingstyle{More Skills}}
    {Leading and working within teams, strong mathematics background, data analysis, Microsoft Office, product research and design}
    
%Leadership and Activities%%%%%%%%%%%
\cvsection{LEADERSHIP AND ACTIVITIES}
\vspace{\cvbetweensectionandheadingextraskipamount}

\cvitem{2015 - Present}
    {Study Abroad in London, England with CAPA Global Health Networt (2018), Executive Board of Alpha Tau Omega Leadership Development Fraternity (2017), Volunteer at Natalie's Second Change Dog Shelter (Present), Eagle Scout and Avid Backpacker (Present)}

\end{document}